---
title: "PSTAT 10 Worksheet 2"
subtitle: "Due 6/26/2024 11:59pm"
output: pdf_document
---

# Problem 1: Basic vector manipulation

1. Recall from lecture my 2023 monthly gas bill in order was given by:

```{r}
gasbill <- c(46, 33, 39, 37, 46, 30, 48, 32, 49, 35, 30, 48)
```

It turns out the charge for December should have been 49 instead of 48. Update 
the ```gasbill``` to reflect the true charge. Try not to “cheat” and just type 
in all the old values again; use the existing ```gasbill``` vector.

```{r}
gasbill[12] <- 49
gasbill
```

2. Recreate the following numeric vector. Avoid typing in all of the values manually.

```{r}
## [1] -50 -51 -52 -53 -54 -53 -52 -51 -50
x <- c(-50:-54 , -53:-50)
x
```

3. Create a vector from 1 to 10 with increments of 0.05. What is the length of this vector? Hint: Use `seq` with `by` argument.
```{r}
y <- seq(1, 10, 0.05)
y
length(y)
```
Length of the vector is 181. 

4. Create a vector of length 100 from 1 to 10 with uniform increments. What is the increment? Hint: Use `seq` with `length` argument.
```{r}
z <- seq(1, 10, length=100)
z
length(z)
z[2]-z[1]
```
Increment is 0.09090909.

5. What happens if you try to use `seq` with both the `length` and `by` arguments specified?
```{r, eval = FALSE}
w <- seq(1, 10, length = 91)
```
If the above chunk is run, we get the error "Error in seq.default(1, 10, by = 1, length = 1) : too many arguments". For seq,
we can only specify either by or length. 

# Problem 2

Download the file `ws2.csv` from the course website and import it into R. This data set has two variables named `x` and `y`.

Make sure to change your `here()` function to point to your `ws2.csv` file.

```{r}
library(here)
ws2_df <- read.csv(here("week1_files", "ws2.csv"))
summary(ws2_df)
```

Remember the variables in a data frame are accessed by name with the dollar sign (and that the result is a vector).

1. Determine the lengths of x and y.
```{r}
length(ws2_df$x)
length(ws2_df$y)
```
The lengths of both x and y are 100.

2. What is the 40th element of x and the 80th element of y?
```{r}
ws2_df$x[40]
ws2_df$y[80]
```
The 40th element of x is 30. The 80th element of y is 42.

3. What is the average of all the values in the data frame, including both x and y?
```{r}
mean(c(ws2_df$x, ws2_df$y))
```
The average of all the values in the data frame is 51.02.

4. How many elements of x are greater than 70?
```{r}
length(ws2_df$x[ws2_df$x>70])
```
24 elements of x are greater than 70.

Let’s look at the first 4 elements of x and y:

```{r}
ws2_df$x[1:4]
## [1] 74 89 78 23
ws2_df$y[1:4]
## [1] 58 26 48 80
```

The first three elements of x are greater than or equal to their corresponding 
element in y: $74 > 58$, $89 > 26$, $78 > 48$. But the fourth element of `x`, 
23, is less than the fourth element of `y`, 80.

5. How many elements of x are greater than or equal to the corresponding element in y?
```{r}
length(ws2_df$x[ws2_df$x > ws2_df$y])
```
45 elements of x are greater than or equal to the corresponding element in y. 

6. What is the proportion of elements of x that are greater than or equal to the corresponding element in
y?
```{r}
length(ws2_df$x[ws2_df$x >= ws2_df$y])/length(ws2_df$x)
```
0.46 of the elements of x are greater than or equal to the corresponding element in y. 

7. How many values in x differ from their corresponding value in y by more than 10 in absolute value?
Hint: there is an `abs` function.
```{r}
length(ws2_df$x[abs(ws2_df$x - ws2_df$y)])
```
99 values in x differ from the corresponding value in y by more than 10 in absolute value. 

# Problem 3

Create a vector of integers from 1 to 12 inclusive.
```{r}
a <- 1:12
a
```

1. Use the vector to create a 3x4 matrix. Did recycling occur?
```{r}
b <- matrix(a, nrow = 3, ncol = 4)
b
```
Recycling did not occur.

2. Use the vector to create a 4x4 matrix. Did recycling occur?
```{r}
c <- matrix(a, nrow = 4, ncol = 4)
c
```
Recycling did occur. 

# Problem 4

Use the heights_df data frame from worksheet 1. The height variable is given in centimeters (cm).

1. Write a vectorized function cm_to_inch that takes a numeric centimeter and converts it to inches.
```{r}
heights_df <- read.csv(here("week1_files", "heights.csv"))

cm_to_inch <- function(cm)
{
  inch <- cm * 0.3937
  return(inch)
}
```

Apply the function to the height vector. First 10 elements are shown below:

```{r, eval= FALSE}
head(cm_to_inch(heights_df$height), 10) # the head function gives the first elements
## [1] 62.40 67.08 65.52 71.37 68.25 73.71 60.84 65.13 76.05 64.35
```

2. Write a vectorized function cm_to_ft_inch that converts numerical values given in cm to a feet inch format, rounding to the nearest inch.
For example,

```{r}
cm_to_ft_inch <- function(cm)
{
  inch = cm_to_inch(cm)
  feet = inch %/% 12
  inch = inch %% 12
  return(paste(feet, round(inch), sep = " ", collapse = NULL)) 
}

cm_to_ft_inch(178)
## [1] "5 9"
```

You may need the (vectorized) quotient function %/% and the remainder function %%:

```{r}
# Quotient: 3 goes into 7 two times
7 %/% 3
## [1] 2
# Remainder: The remainder when 7 is divided by 3 is one
7 %% 3
## [1] 1
```

Remember you should look things up on StackOverflow if you’re stuck with some operations.
Apply the function to the height vector.

```{r}
head(cm_to_ft_inch(heights_df$height), 10)
## [1] "5 2" "5 7" "5 6" "5 11" "5 8" "6 2" "5 1" "5 5" "6 4" "5 4"
```