---
title: "PSTAT 10 Worksheet 7"
output:
  pdf_document:
    latex_engine: xelatex
---

## Setup
```{r}
library(RSQLite)
library(sqldf)
library(DBI)
chinook_db <- dbConnect(SQLite(), "Chinook_Sqlite.sqlite")
dbExecute(chinook_db, "pragma foreign_keys = on")
set.seed(1)
```


## Problem 1

1. Primary and foreign keys are used to model relations between data sets. Specifically, they are used to link related observations
in different data sets together to show that they have a real world connection. 

2. Relational databases use relations between primary and foreign keys to represent relations between different sets of 
data. For example, a data set containing data on student grades would be related to a data set on personal information
through a common key such as a student ID. 

3. SQL is a standardized language used to work with relational databases. It can be implemented in different relational 
database systems, or RDBSs. SQLite is a lightweight, serverless RDMS that implements SQL-compatible syntax. It is an 
*implementation* of SQL in a RDBS. RSQLite is an R package that implements an interface between R and a SQLite implementation. 
It provides functions for R to run SQLite queries on SQLite databases.  


## Problem 2

```{r}
dbListTables(chinook_db)
dbGetQuery(chinook_db, "pragma foreign_key_list(Album)")      
dbGetQuery(chinook_db, "pragma foreign_key_list(Artist)")      
dbGetQuery(chinook_db, "pragma foreign_key_list(Customer)")      
dbGetQuery(chinook_db, "pragma foreign_key_list(Employee)")      
dbGetQuery(chinook_db, "pragma foreign_key_list(Genre)")      
dbGetQuery(chinook_db, "pragma foreign_key_list(Invoice)")      
dbGetQuery(chinook_db, "pragma foreign_key_list(InvoiceLine)")      
dbGetQuery(chinook_db, "pragma foreign_key_list(MediaType)")      
dbGetQuery(chinook_db, "pragma foreign_key_list(Playlist)")      
dbGetQuery(chinook_db, "pragma foreign_key_list(PlaylistTrack)")      
dbGetQuery(chinook_db, "pragma foreign_key_list(Track)")      
```
The foreign key relations are: \newline
Album.ArtistId -> Artist.ArtistId \newline
Customer.EmployeeId -> Employee.SupportRepId \newline
Employee.ReportsTo -> Employee.EmployeeId\newline
Invoice.CustomerId -> Customer.CustomerId \newline
InvoiceLine.TrackId -> Track.TrackId \newline
InvoiceLine.InvoiceId -> Invoice.InvoiceId   \newline
PlaylistTrack.TrackId -> Track.TrackId \newline
PlaylistTrack.PlaylistId -> Playlist.PlaylistId  \newline
Track.MediaTypeId -> MediaType.MediaTypeId \newline
Track.GenreId -> Genre.GenreId \newline
Track.AlbumId -> Album.AlbumId \newline


## Problem 3

1. 

```{r}
dbGetQuery(chinook_db, "SELECT CustomerId, FirstName, LastName, State, Country
                        FROM Customer 
                        WHERE State='CA'")
```

2. 

```{r}
dbGetQuery(chinook_db, "SELECT count(*)
                        FROM Customer
                        WHERE Country='Brazil'")
```
There are 5 customers from Brazil. 