---
title: "Homework 2"
output: pdf_document
---

# Problem 1
```{r}
x <- 1:100
e_limit <- vector(length = length(x))
e_limit[1] <- 1
e_series <- vector(length = length(x))
e_series[1] <- 2

for(i in 2:100)
{
    e_limit[i] <- (1 + (1/i))^i
    e_series[i] <- (1/factorial(i))+e_series[i-1]
}

plot(x, e_limit[x], col='blue', type='l', 
main='Convergence to e', xlab='x', ylab='y')
lines(x, e_series[x], col='red')
legend("bottomright",
  legend = c("Limit", "Series"),
  col = c("blue", "red"),
  lty = c(1,1)
)
```

## Problem 2
```{r}
library(nycflights13)
library(tidyverse)
```

1.
```{r eval=FALSE}
print(flights)
? flights
```
Flights is a dataset containing all the flights that have departed NYC 
in 2013. It is a tibble with 19 variables, including info on the date of 
each flight (i.e. year, month, and day), departure time (dep_time), and arrival
time (arr_time). \newpage

2. 
```{r}
count(flights |> filter((carrier == 'AA') & (dep_time < 1030)) |>
select(month, day, dep_time, dest, carrier))
```
11,378 flights fit this criteria. \newline

3. 
```{r}
sum((flights |> filter(month == 12 & day == 25 & year == 2013))$distance)
```
Across all flights, 803,747 miles were traveled. \newline

4. 
```{r}
flights |> filter(month == 12 & day == 25 & year == 2013) |>
mutate(air_time_hour = air_time/60)  |> select(month, day, origin, dest, air_time_hour)
```

## Problem 3

```{r}
library(datasets)
```

1. 
```{r eval=FALSE}
print(mtcars)
? mtcars
```
This dataset contains data from the 1974 Motor Trend US magazine on 
fuel consumption and 10 aspects of automobile design and performane for 
32 cars. It is not a tibble. It has 11 variables, including miles per gallon
(mpg) and horsepower (hp). 

2. 
```{r}
hist(mtcars$disp, plot=TRUE, breaks=seq(0,500,25), main="Hist of Displacement", xlab="Displacement (cu. in.)", ylab="Frequency")
abline(v=c(mean(mtcars$disp), median(mtcars$disp)), col="red", lty=c(2,3), lwd=c(2,1))
legend("topright",
  legend = c("mean disp", "median disp"),
  col = c("red", "red"),
  lty = c(2,3),
  lwd(2,1)
)
```

3. 
```{r}
boxplot(qsec ~ cyl, data=mtcars, xlab="Number of Cylinders", ylab="1/4 mile time (sec)")
```
The outlier is the Merc 230. \newpage

4. 
```{r}
barplot(table(mtcars$cyl), xlab="Number of cylinders", ylab = "Count")
```

## Problem 4

```{r}
search_insert_position <- function(v, target)
{
    for(i in 1:length(v))
    {
        if(v[i] >= target)
        {
            return(i) 
        }
    }
    return(length(v)+1)
}

x <- c(1,3,5,6)
search_insert_position(x, 5)
search_insert_position(x, 2)
search_insert_position(x, 7)
```

